---
title: "pooled estimate comparison"
author: "Andrew Mertens"
date: "June 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(metafor)
df <- readRDS(file=here("results/pooled_results.Rdata"))
df$cat <- factor(df$cat, levels=c("Overall", "Everyday Public Conservation", "Household conservation", "Green consumerism", "FFA" ))
df$type <- factor(df$type, levels=c("Subjective only","Subjective + Descriptive","Subjective + Personal", "Subjective, Descriptive, + Personal"))
df$normcat <- factor(df$normcat, levels=c("Subjective","Descriptive","Personal"))

```

## Is the overall pooled estimate for subjective-norms-only different from the overall estimate for subjective norms when other norms are included?


```{r, echo=F}
df.overall <- df %>% filter(cat=="Overall" & (normcat=="Subjective" | is.na(normcat)))

#rma.mv(est, vi, mods = ~ type, random = ~ type | id, struct="DIAG", data=df.overall, digits=3)
res1 <- rma(yi=est, vi=vi, mods = ~ type, method="FE", data=df.overall, digits=3)
res1
```


## Comparing categories within subjective only

```{r, echo=F}
df.subjective <- df %>% filter(type=="Subjective only") 
res2 <- rma(yi=est, vi=vi, mods = ~ cat, method="FE", data=df.subjective, digits=3)
res2
```

## Comparing subjective, descriptive, personal within ("subjective " is the reference category) 

### Subjective + Descriptive

##### Overall


```{r, echo=F}
df.SD <- df %>% filter(type=="Subjective + Descriptive")
unique(df.SD$cat)
resSD_overall <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.SD[df.SD$cat=="Overall",], digits=3)
resSD_overall
```


### Subjective + Personal

##### Overall

```{r, echo=F}
df.SP <- df %>% filter(type=="Subjective + Personal")
unique(df.SP$cat)
resSP_overall <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.SP[df.SP$cat=="Overall",], digits=3)
resSP_overall
```

##### Household conservation

```{r, echo=F}
resSP_HC <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.SP[df.SP$cat=="Household conservation",], digits=3)
resSP_HC
```

##### Green consumerism

```{r, echo=F}
resSP_GC <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.SP[df.SP$cat=="Green consumerism",], digits=3)
resSP_GC
```

##### FFA

```{r, echo=F}
resSP_FFA <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.SP[df.SP$cat=="FFA",], digits=3)
resSP_FFA
```

# Subjective, Descriptive, + Personal

##### Overall


```{r, echo=F}
df.all <- df %>% filter(type=="Subjective, Descriptive, + Personal")
unique(df.all$cat)
resall_overall <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.all[df.all$cat=="Overall",], digits=3)
resall_overall
```

##### Household conservation

```{r, echo=F}
resall_HC <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.all[df.all$cat=="Household conservation",], digits=3)
resall_HC
```

##### Green consumerism

```{r, echo=F}
resall_GC <- rma(yi=est, vi=vi, mods = ~ normcat, method="FE", data=df.all[df.all$cat=="Green consumerism",], digits=3)
resall_GC
```

